\documentclass[10pt,twoside,twocolumn,openany,bg=print]{dndbook}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{hang}
\usepackage{listings}
\usepackage[hidelinks]{hyperref}

\lstset{%
  basicstyle=\ttfamily,
  language=[LaTeX]{TeX},
}

% Start document
\begin{document}

% Comment this out if you're using the article class.
\chapter{Waterdeep Dragon Heist - Player Guide}

\section{Session Zero}

The goal for Session Zero is to come up with a basic idea of your backstory, and nail down the core aspects of your character (race, class, background). This can always be fleshed out more as you play.

\subsubsection{Step 1: Who are you?}
The first step is to establish a character concept. This is the elevator pitch for your character. It can be one sentence, or even just a few words. An honorable thief. A noble who lost their lands. A scholar with a drinking problem. This idea is what will drive the rest of your decisions in building your character.

\subsubsection{Step 2: How did you get to this point?}
Try to come up with two or three “defining moments” from your character’s past. It could be the moment you first met your spouse, the day you left your hometown, or the first time you killed someone. It’s okay to be vague here. Just try to think about what might have led to who you are today.

\subsubsection{Step 3: Why are you in Waterdeep?}
This campaign takes places entirely in the city of Waterdeep so it’s important to establish what brings you to the city, why you would stay, and importantly, why you would join up with a group of strangers. See the next page for a quick guide to the city if you need a better idea of the city itself.

\begin{quotebox}
    \textbf{A word of advice!} As you create your character concept, consider that this campaign takes place in a densely-populated urban metropolis, where openly wielding weapons or magic on the streets can quickly land you in a jail cell. Combat isn’t always the solution, and not all combat has to be lethal.
\end{quotebox}

\begin{paperbox}[float=!t]{Additional Resources}
\begin{itemize}
    \item Random character generator for inspiration \url{https://trwolfe13.github.io/tiyl/}
    \item Which class should you play? (Flowchart) \url{https://preview.tinyurl.com/yd4wzzgq}
    \item 5 Steps to Writing a Killer RPG Character Backstory (Geek \& Sundry) - \url{https://preview.tinyurl.com/ybkyqkzr}
    \item 20 questions to help you create a backstory for your character (Reddit) - \url{https://preview.tinyurl.com/oljh8rl}
    \item 34 Questions to Ask When You're Stumped on Your Backstory (Reddit) \url{https://preview.tinyurl.com/y777u35x}
\end{itemize}
\end{paperbox}

\begin{quotebox}
If you have access to the Xanathar's Guide To Everything, you can get a lot of inspiration from the "This Is Your Life" section on page 61-73.
\end{quotebox}

\subsection{Choosing a background}

This part of character creation is probably best done \textbf{at} Session Zero together as a group, so you can bounce ideas off each other to make sure you’re a well-rounded group in terms of skills and abilities. The following info is meant to provide a mechanical structure around the character concept you have in mind, but don’t feel limited by the options presented. We can always customize as needed!

A background will help guide how you pick the following:
\begin{itemize}
\item Two personality traits (Slow to anger, quick to laugh)
\item One ideal that drives your character (Family, loyalty, or honor)
\item One bond that represents your connection to the world (Finding a lost artifact)
\item One flaw (Claustrophobic, gambling addict, gullible, brash)
\end{itemize}
See Appendix A for a list of backgrounds.

\pagebreak

\chapter{A Brief Guide to Waterdeep}
Waterdeep is a bustling, crowded, busy mercantile city where coin is king and tolerance for people of all races and religion is high. Waterdhavians live life at a fast pace, and despite their fervent work ethic, they rarely miss an opportunity to celebrate, with festivals often going on all day and all night. In Waterdeep, wealth brings respect, respect earns influence, and influence is power.

\section{City Life}
\begin{description}
\item [Government]
The city is governed by the Masked Lords, an anonymous group of representatives who are in turn led by the Open Lord of Waterdeep.
\item [Economy]
Economic activity in Waterdeep has been dominated by the city’s dozens of guilds for more than three centuries, and virtually all commerce flows through them.
\item [Law]
The City Watch enforces the day-today law in the city, while the Magisters act as judge and jury. Both are swift to mete out justice as needed and are guided by the Code Legal.
\item [Military]
The City Guard (and its famed griffon-riders) defends the city from outside threats, along with the Watchful Order of Magists and Protectors.
\end{description}

\section{Places \& Landmarks}
\begin{description}
\item [Yawning Portal Inn]
Waterdeep’s most famous inn, named for the large “well” within its walls that down into the dungeon of Undermountain. A common destination for would-be heroes.
\item [Walking Statues]
These 100-ft tall statues were built as a defense mechanism of the city, but once wreaked havoc due to a magical disaster years ago. They’ve since laid dormant.
\item [Wards of Waterdeep]
The city is divided roughly into 8 wards, each of which serves its own purpose. The Castle Ward is the seat of government, the Trade Ward the center of commerce, and so on.
\end{description}

\section{Important People}
\begin{description}
\item [Laeral Silverhand]
The current Open Lord of Waterdeep. Helped oust Dagult Neverember.
\item [Dagult Neverember]
The previous Open Lord. Removed from power and exiled for corruption
\item [Vajra ‘Blackstaff’ Safahr]
Archwizard of Waterdeep, leads Force Grey (see factions)
\item [Durnan]
Runs the Yawning Portal Inn. Former adventurer, well beyond the typical human age.
\item [Volothamp Geddarm]
A legendary traveler and storyteller, most famous for his guidebooks.
\end{description}

\section{Factions}
\begin{description}
\item [Emerald Enclave]
Opposes threats to the natural world, but recognizes the need for balance between civilization and nature. Many of its members are druids, rangers, or those who worship nature.
\item [Force Grey (or Gray Hands)]
Elite adventurers who work for the government of Waterdeep.
\item [Harpers]
A semi-secret organization dedicated to promoting good, preserving history and maintaining a balance between civilization and nature. Has spies placed in cities across the realm.
\item [Lord’s Alliance]
A coalition of rulers from cities across Faerûn, who collectively agree that some solidarity is needed to keep evil at bay. Includes Neverwinter, Waterdeep, Baldur’s Gate, and others.
\item [Order of the Gauntlet]
Formed to destroy evil in the world at large. Many members are paladins, clerics, or monks.
\item [Zhentarim]
An affiliation of merchants and mercenaries known for their cutthroat tactics. Rumors have emerged of a schism among their members in Waterdeep.
\end{description}

\onecolumn

\chapter{Appendix A: Backgrounds}

PHB = Player's Handbook, SCAG = Sword Coast Adventurer's Guide

\header{Backgrounds}

\begin{dndtable}[XXXXX]
    \textbf{Name}           & \textbf{Source}   & \textbf{Skills}                                                               & \textbf{Languages}    & \textbf{Tools} \\
    Acolyte                 & PHB               & Insight (WIS), religion (INT)                                                 & Any x2                & None  \\
    Charlatan               & PHB               & Deception (CHA), sleight of hand (DEX)                                        & None                  & Disguise kit, forgery kit  \\
    City Watch              & SCAG              & Athletics (STR), insight (WIS)                                                & Any x2                & None  \\
    Clan Crafter            & SCAG              & History (INT), insight (WIS)                                                  & Any x1                & Artisan's tools x1  \\
    Cloistered Scholar      & SCAG              & History (INT), and choose 1: arcana (INT), nature (INT), religion (INT)       & Any x2                & None  \\
    Courtier                & SCAG              & Insight (WIS), persuasion (CHA)                                               & Any x2                & None  \\
    Criminal                & PHB               & Deception (CHA), stealth (DEX)                                                & None                  & Gaming set x1, thieves' tools \\
    Entertainer             & PHB               & Acrobatics (DEX), performance (CHA)                                           & None                  & Disguise kit, musical instrument x1   \\
    Faction Agent           & SCAG              & Insight (WIS), and choose 1: special (See page)                               & Any x2                & None  \\
    Far Traveler            & SCAG              & Insight (WIS), perception (WIS)                                               & Any x1                & Choose 1: musical instrument x1, gaming set x1    \\
    Folk Hero               & PHB               & Animal handling (WIS), survival (WIS)                                         & None                  & Artisan's tools x1, vehicles (land)   \\
    Gladiator               & PHB               & Acrobatics (DEX), performance (CHA)                                           & None                  & Disguise kit, unusual weapon x1   \\
    Guild Artisan           & PHB               & Insight (WIS), persuasion (CHA)                                               & Any x1                & Artisan's tools x1    \\
    Guild Merchant          & PHB               & Insight (WIS), persuasion (CHA)                                               & Any x1                & Navigator's tools \\
    Hermit                  & PHB               & Medicine (WIS), religion (INT)                                                & Any x1                & Herbalism kit \\
    Inheritor               & SCAG              & Survival (WIS), and choose 1: arcana (INT), history (INT), religion (INT)     & None                  & Gaming set x1, musical instrument x1  \\
    Investigator            & SCAG              & Insight (WIS), investigation (INT)                                            & Any x2                & None  \\
\end{dndtable}

\pagebreak

\header{Backgrounds}

\begin{dndtable}[XXXXX]
    \textbf{Name}           & \textbf{Source}   & \textbf{Skills}                                                               & \textbf{Languages}    & \textbf{Tools} \\
    Knight                  & PHB               & History (INT), persuasion (CHA)                                               & Any x1                & Gaming set x1 \\
    Knight of the Order     & SCAG              & Persuasion (CHA), and choose 1: special (See page)                            & Any x1                & Choose 1: gaming set x1, musical instrument x1    \\
    Mercenary Veteran       & SCAG              & Athletics (STR), persuasion (CHA)                                             & None                  & Gaming set x1, vehicles (land)    \\
    Noble                   & PHB               & History (INT), persuasion (CHA)                                               & Any x1                & Gaming set x1 \\
    Outlander               & PHB               & Athletics (STR), survival (WIS)                                               & Any x1                & Musical instrument x1 \\
    Pirate                  & PHB               & Athletics (STR), perception (WIS)                                             & None                  & Navigator's tools, vehicles (water)   \\
    Sage                    & PHB               & Arcana (INT), history (INT)                                                   & Any x2                & None  \\
    Sailor                  & PHB               & Athletics (STR), perception (WIS)                                             & None                  & Navigator's tools, vehicles (water)   \\
    Soldier                 & PHB               & Athletics (STR), intimidation (CHA)                                           & None                  & Gaming set x1, vehicles (land)    \\
    Spy                     & PHB               & Deception (CHA), stealth (DEX)                                                & None                  & Gaming set x1, thieves' tools \\
    Urban Bounty Hunter     & SCAG              & Choose 2: deception (CHA), insight (WIS), persuasion (CHA), stealth (DEX)     & None                  & Choose 2: gaming set x1, musical instrument x1, thieves' tools    \\
    Urchin                  & PHB               & Sleight of hand (DEX), stealth (DEX)                                          & None                  & Disguise kit, thieves' tools  \\
    Uthgardt Tribe Member   & SCAG              & Athletics (STR), survival (WIS)                                               & Any x1                & Choose 1: artisan's tools x1, musical instrument x1   \\
    Waterdhavian Noble      & SCAG              & History (INT), persuasion (CHA)                                               & Any x1                & Choose 1: gaming set x1, musical instrument x1    \\
\end{dndtable}
% End document
\end{document}
